\section{My Biography}
Emily Hackett biography for the Pawsey Supercomputing Centre Summer Internship
\subsection{About me}
I am a third year Bachelor of Philosophy (Honours) student at University of Western Australia who has just finished a major in physics. Next year I plan to do honours, likely in computational physics, but with a medical application. The year after that I may be beginning a post-graduate medical degree, which I have an assured entry for. 
I am doing a joint ICRAR/Pawsey studentship this summer, working with Dr Chris Power and Dr Charlotte Welker on data from the Horizon-AGN large scale hydrodynamical cosmological simulation. Using code developed by a previous PhD student, the properties of stellar halos around galaxies can be extracted from the simulation data. Previous research has investigated the correlation between properties of dark matter halos (within which galaxies form) with the large scale structure of the cosmic web that they reside (their local environment). This project looks to see how the properties of the stellar halos similarly relate to this local environment - the orientation and properties of the cosmic web.
My aim for this studentship is to improve on my programming and computing skills, as well as gain a new set of introductory skills in the areas of parallel programming and super computing. I also want to learn more about the eResearch environment: how students fit in to it, how collaborations occur between people and between organisations (including universities), the etiquette involved, and more generally about the resources that are actively available to researchers (even student researchers) in these sorts of areas.

