\section{Paczki}
Paczki are pastries traditional to Polish cuisine. They are similar to doughnuts.
\section{Ingredients:}
\begin{itemize}
\item 1 1/2 cups all purpose flour
\item 1/4 cup sugar
\item 1/4 teaspoon salt
\item 2 teaspoons (1 packet $=$ 7 grams) yeast (instant or regular)
\item 2/3 cup 1\%milk - warmed to $120\,^{\circ}\mathrm{F}$ for instant/$110\,^{\circ}\mathrm{F}$ for regular yeast
\item 3 Tablespoons oil (canola or extra light)
\item 2 egg yolks
\item 1/2 teaspoon vanilla
\item about 1/4 cup extra flour
\\

\item 1 Tablespoon melted butter
\item 1/3 cup sugar for coating
\item 1 cup thick jam, custard, or filling of choice
\end{itemize}

\section{Instructions:}
\begin{enumerate}
\item Place flour, sugar, salt and yeast in a large bowl.
\item Stir in warm milk, followed by oil, egg yolks and vanilla.
\item With electric mixer, beat for 2 minutes on high speed.
\item Stir in enough flour until dough holds together.
\item Place dough on a floured surface and knead 50 times, cover 
with plastic and let rest 10 minutes.
\item If using custard filling, make it now so it can coll. 
(see recipe below)
\item Line a large baking sheet with parchment paper
\item On a floured surface, roll dough 1/2-inch thick. Cut circles 
using a 2 1/2-inch round cutter, dipped in flour. Re-roll scraps.
\item Place mound on baking sheet, cover with a towel and let rise 
in a warm spot about 45 minutes. (1 hour at room temperature) 
After 30 minutes, preheat oven to $375\,^{\circ}\mathrm{F}$.
\item When paczki are puffy, but not necessarily doubled in size, 
bake for 10 minutes.
\item Meantime, melt butter and place 1/3 cup sugar in a plastic 
produce bag, and lay down dome wax paper to save cleanup.
\item Removepaczki immediately from pan to wax paper. Brush each 
one while warm (top \& sides) with melted butter and roll in 
bag to coat with sugar. Shake off excess.
\item Fill using a pastry bag with a long slender tip, pushing 
into the side. \emph{Serve immediately!}

\emph{Custard Filling}
\item In a small saucepan, combine 1/4 cup sugar + 1 Tablespoon 
cornstarch. Slowly stir in 1 cup 1\% milk + 1 egg yolk. Bring 
to a boil and cook about a minute, stirring constantly, until 
thickened. (it thickens more as it cools) Transfer to a plate 
and let it stand, undisturbed, to cool thoroughly before using 
\- refrigerate if necessary.
\item Fill paczki with filling using a pastry bag with a long 
slender tip pushing into the side or slice an opening the 
side and insert filling with a spoon. \\
\emph{Serve immediately.} 

\end{enumerate}
