\section{Spinach, feta and broad bean pie}
This fabulous vegetarian pie contains broad beans, fetta cheese and spinach in a crunchy wholemeal pastry.
\section{Ingredients:}
\begin{itemize}
	\item 2 cups wholemeal plain flour
	\item 1 cup wheatgerm
	\item 160g butter, chilled, chopped
	\item 4 eggs
	\item 2 tablespoons chilled water
	\item 2 teaspoons olive oil
	\item 1 large brown onion, finely chopped
	\item 2 garlic cloves, crushed
	\item 200g baby spinach
	\item 2 cups (300g) fresh broad beans
	\item 100g feta, crumbed
	\item 2 tablespoons finely grates hard cheese or parmesan
	\item 1 tablespoon chopped fresh dill
	\item 1 teaspoon finely grated lemon rind
	\item 1/3 cup milk
\end{itemize}

\section{Instructions:}
\begin{enumerate}
\item Place flour, wheatgerm and butter in a food processor. Process until mixture resembles fine breadcrumbs. Add 1 egg and chilled water. Process until mixture just comes together and forms a soft dough, adding extra water if necessary. Turn out onto a lightly floured surface. Knead until smooth. Shape into a disc. Wrap in plastic wrap. Refrigerate 30 minutes or until firm.
\item Meanwhile, heat oil in a large, deep frying pan over medium-high heat. Add onion. Cook for 5 minutes or until softened. Add garlic. Cook, stirring, for 1 minute or until fragrant. Add spinach. Cook for 2 minutes or until wilted. Transfer mixture to a colander over a bowl to strain. Cool for 10 minutes.
\item Place broad beans in a heatproof bowl. Cover with boiling water. Set aside for 30 seconds. Drain. Refresh in a bowl of chilled water. Drain. Peel and discard skins.
\item Preheat oven to 190C/170C fan-forced. Roll pastry out between 2 sheets of baking paper until 5mm thick. Line a 4cm-deep, 22cm (top) pie plate with pastry. Trim excess. Pinch edge of pastry to form a decorative pattern.
\item Place spinach mixture in a bowl. Add broad beans, fetta, cheese, dill and lemon rind. Whisk milk and remaining eggs together. Add to broad bean mixture. Season with salt and pepper. Stir until well combined. Spoon mixture into pastry case. Place on a baking tray. Bake for 45 minutes or until golden and filling has set. Stand for 10 minutes. Cut into wedges. Serve.
\end{enumerate}
